An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-25 Revision/response.tex

\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_}
\texttt{description} field as real attributes, applying them in both attribute filtering and range filtering experiments.

\textcolor{blue}{
	"Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes. It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute."
}
%%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%

\myfbox{
	\begin{metarevision}
		\textit{Evaluate if the server setting affects the relative ordering of methods in experiments}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
That is a great suggestion. In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency and smaller RAM capacity of the Xeon 6330 processors. \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}

Attribute filtering:
%\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b. Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}

Range filtering:
%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b. When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results."}
\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b. Our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results."}

### 2025-07-25 VLDB2026/main.tex
1

	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios. The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance. This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.

	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes. In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios. However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.

>>>>

	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios. The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance. This highlights its \textcolor{red}{robustness}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.

	\textcolor{red}{iRange and Faiss} offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes. In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios. However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
